---
title: "interactivity_lecture"
author: "mggn"
date: "10/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Website is a collection of pages written in HTML that is hosted on a server and is retrievable
Let's make a website to disseminate a project!
Lol Jeff is talking about dial up
We don't need to know HTML because we use rmarkdown
I guess we can write a website using R
Knowing RMD is half the battle
  -need to host it for other people to see
  -repo = website
  -aka github allows you to host websites for free
Workflow is similar to working with our rmd, but we need to tell github that
the repo is a website
github.io
landing page HAS TO BE CALLED index.Rmd
The class has a 

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
